Concordance between observations and simulations in the evolution of the mass relation between supermassive black holes and their host galaxies

### 2022-04-08 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
draft updated

\begin{abstract}
We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh --\smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model). The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. To make fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations. Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation. 
Regarding the mean scaling relation, Horizon-AGN and TNG are in closest agreement with the observational data at both low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties. 
For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and thus closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow. The consistency in the dispersion with redshift in our analysis lends support to the importance of both quasar and radio mode feedback prescriptions in the simulations. Finally, we investigate evolution as a function of stellar and \red{BH} mass, and argue that the most direct way to probe the co-evolution of galaxies and \red{BH}s is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.

@@

\section{Introduction} \label{sec:intro}
\todo{Re-read to avoid residual P1.}
The close correlations between \red{the mass of} supermassive black holes (\red{\mbh}) and the properties of their host galaxies (e.g., stellar mass\red{, \smass}) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Tre++04,Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}. While, an {\it observed} evolution has been found \red{at redshift range xxx} in many studies \todo{move ref} in which the growth of BHs predates that of the host, other studies predict \todo{move ref} that BHs grow commensurately with galaxies.
However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15}.

Various theoretical models have been proposed to explain the origin of the scaling relations. For example, AGN feedback is considered as one of the possible viable mechanisms. During this process, a fraction of the AGN energy is injected into its surrounding gas, which can then regulate the mass growth of the BH and its host. In this scenario, star formation is inhibited by the heating and unbinding of a significant amount of gas. Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}. Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}. However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ compared to what is observed today.

Numerical simulations provide an opportunity to further understand the connection between BHs and their host galaxies. For example, a comparison of scaling relations has been made using state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host). Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, 
including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH \red{simulations~\citep{Schaye2015, Crain2015, McAlpine2016},} Illustris moving-mesh \red{simulation~\citep{Genel2014, 2014MNRAS.444.1518V, Sijacki2015, Nelson2015, Li2019}} and the SIMBA \red{simulation~\citep{Thomas2019, Dave2019}. }
In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}. However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range (i.e., limited to the local universe).

@@

\subsection{SDSS/HSC sample}\label{sec:hsc}
A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}. With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been \red{performed \citep[][]{Li2021a}} to obtain the flux and color of each quasar's host galaxy. The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task. This approach is first developed by~\citet{Ding2020} and used to decompose the near-infrared emission of the HST sample (see next section). Having measured the host light in each band, the stellar mass of host galaxy is derived using spectral energy distribution (SED) fitting with CIGALE~\citep{Boquien2019}. Simulation tests are also performed to verify the fidelity of the \smass\ measurements. The statistical measurement error on \smass\ is at the $\sim$0.2~dex level. The values of \mbh\ are determined by~\citet{Rakshit2020} which are estimated based on the \hbeta-based measurements using the virial method~\citep{Peterson2004, Vestergaard2006}. The typical error of \mbh\ are estimated to be 0.4 dex. We refer the reader to~\citet{Li2021a} in the Section~4.2 for more details.

@@

A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS). HSC/WFC3 IR camera is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six position dither pattern and a total exposure time $\sim$2348~s. The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target to bracket the 4000~\AA~break.  The AGN images are analyzed and decomposed to infer the host galaxies fluxes using the approach developed by D20 based on {\tt lenstronomy}. The HST ACS/F814W imaging data for 21/32 of the AGNs is also used to infer the host color. The results show that stellar templates of 1 and 0.625~Gyr can match the sample color at $z<1.44$ and $z>1.44$, respectively (see Figure 5 in D20). These best-fit models are used to estimate the stellar masses of the host galaxies. \mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citet{Vestergaard2006}, in a consistent manner to that adopted for HSC sample. We refer the reader to D20 for a more detailed description of the analysis.

@@

\begin{deluxetable*}{lccccc}
\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
}
\startdata
box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
\cline{1-6}
{\bf mass resolution} \\
 dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
 baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
\cline{1-6}
{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
Low acc. mode  & -- & 0.35 $\times$ 0.2 & $\leq0.2 \times$ 0.2 & $\leq0.2 \times$ 0.2 & 1 $\times$ 0.1 \\
Transitions btw. modes & -- & 0.05 & \multicolumn{2}{c}{min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]} & 0.01 \\
\cline{1-6}
AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
\enddata
\tablecomments{In the penultimate row, $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$. $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$. \todo{The $\leq$ sign in the low accretion feedback mode of TNG is also not clear. Is it a fixed value or a distribution?} \todo{Please mention whether the same radiative efficiency is used to compute AGN luminosity in all the simulations.}
}
\end{deluxetable*}

@@

\subsection{{\tt MassiveBlackII} (MBII)}\label{subsec:MBII}
MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $(142.7~\mathrm{cMpc})^3$
and $2\times1792^3$ particles. \todo{answer what is the factor 2 here. A twin box with 1793$^3$ each?} The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}. For dark matter and gas, the mass resolutions are $1.57\times 10^7~M_{\odot}$ and $3.14\times 10^6~M_{\odot}$, respectively. The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process~\citep{2005Natur.433..604D}. Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}. Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.

@@

As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass. We adopt this definition of stellar masses for all simulations described in the following sections. Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure. Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within the Petrosian radii in observational studies~\citep{Schaye2015}. For further details of MBII simulation, we refer the reader to~\citet{Khandai2015}.

@@

The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at~(irregular) intervals between which the BH mass grows by a fixed fraction. The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN. As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass, assuming a \cite{2003PASP..115..763C} IMF.

\subsection{IllustrisTNG}
{\it The Next Generation Illustris Simulations} \red{(IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018}} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes. It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations.

@@

The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$. A Salpeter IMF is assumed. Stellar feedback is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.

@@

We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.  Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbours. Only galaxies with more than 50 particles are considered. The galaxy mass corresponds to the total stellar mass of a galaxy identified with this approach. The stellar mass function is shown in \cite{2017MNRAS.467.4739K} to be in good agreement with observations.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.4\textwidth]{HSC_selection_MBII.png}}
{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.4\textwidth]{HST_selection_MBII.png}}
\end{tabular}
\caption{\label{fig:selection}Demonstration of AGN selection using MBII. {\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles). A matched HSC sample is shown by the orange data points. The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space.
{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample. For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines. \todo{No mention of the redshift in Fig.2}
}
\end{figure*}

@@

For dark matter halos that merge with a larger halo, the impact of dynamical friction is assessed to define whether the halo will survive as a satellite or sink to the center of the dominant galaxy which increases its mass. The binary interactions (fly-bys and mergers), among satellite sub-halos, are  also described by the model. In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}. The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; \todo{the link between BH feeding and star formation channels in this sentence is not clear.} (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion). The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase. A Salpeter IMF is adopted in the SAM simulation. A $\Lambda$CDM power spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter 
$\Omega_b=0.04$, a dark energy density parameter $\Omega_\Lambda=0.7$, and a Hubble constant $h$=0.7 is adopted.

>>>>

\begin{abstract}
We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh --\smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model). The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. To make fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations. Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation. 
Regarding the mean scaling relation, Horizon-AGN and TNG are in closest agreement with the observational data at both low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties. 
For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and thus closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow. The consistency in the dispersion with redshift in our analysis lends support to the importance of both quasar and radio mode feedback prescriptions in the simulations. Finally, we investigate evolution as a function of stellar and \red{BH} mass, and argue that the most direct way to probe the co-evolution of galaxies and \red{BH}s is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects. \todo{Check if updated needed.}

@@

\section{Introduction} \label{sec:intro}
\todo{Re-read to avoid residual P1.}
The close correlations between \red{the mass of} supermassive black holes (\red{\mbh}) and the properties of their host galaxies (e.g., stellar mass\red{, \smass}) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over \red{cosmic time}. While, an {\it observed} evolution has been found \red{since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15, Ding2020, 2021arXiv210902751L} in} which the growth of BHs predates that of the host, other studies \red{predict \citep[e.g.,][]{Schramm2013, Sun2015} that} BHs grow commensurately with galaxies.
However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009}.

Various theoretical models have been proposed to explain the origin of the scaling relations. For example, AGN feedback is considered as one of the possible viable mechanisms. During this process, a fraction of the AGN energy is injected into its surrounding gas, which can then regulate the mass growth of the BH and its host. In this scenario, star formation is inhibited by the heating and unbinding of a significant amount of gas. Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common \red{gas supply~\citep{Cen2015, Menci2016, angles_black_2017}. }Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}. However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ compared to what is observed today.

Numerical simulations provide an opportunity to further understand the connection between BHs and their host galaxies. For example, a comparison of scaling relations has been made using state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host). Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, 
including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH \red{simulations~\citep{Schaye2015, Crain2015, McAlpine2016},} Illustris moving-mesh \red{simulation~\citep{Genel2014, 2014MNRAS.444.1518V, Sijacki2015, Nelson2015, Li2019}, the Horizon-AGN simulation~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D, 2016MNRAS.460.2979V}, and the SIMBA simulation~\citep{Thomas2019, Dave2019}. }
In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}. However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range (i.e., limited to the local universe).

@@

\subsection{SDSS/HSC sample}\label{sec:hsc}
A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}. With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been \red{performed \citep[][]{Li2021a}} to obtain the flux and color of each quasar's host galaxy. The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task. This approach is first developed by~\citet{Ding2020} and used to decompose the near-infrared emission of the HST sample (see next section). Having measured the host light in each band, the stellar mass of host galaxy is derived using spectral energy distribution (SED) fitting with CIGALE~\citep{Boquien2019}. Simulation tests are also performed to verify the fidelity of the \smass\ measurements. The statistical measurement error on \smass\ is at the $\sim$0.2~dex level. The values of \mbh\ are determined by~\citet{Rakshit2020} which are estimated based on the \hbeta-based measurements using the virial method~\citep{Peterson2004, Vestergaard2006}. The typical error of \mbh\ are estimated to be 0.4 dex. \red{The mass ranges for the entire sample are log(\smass) $\in$ [9.0, 11.5] $M_{\odot}$, and log(\mbh) $\in$  [6.5, 10.0] $M_{\odot}$)}.
 We refer the reader to~\citet{Li2021a} in the Section~4.2 for more details.

@@

A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS). HSC/WFC3 IR camera is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six position dither pattern and a total exposure time $\sim$2348~s. The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target to bracket the 4000~\AA~break.  The AGN images are analyzed and decomposed to infer the host galaxies fluxes using the approach developed by D20 based on {\tt lenstronomy}. The HST ACS/F814W imaging data for 21/32 of the AGNs is also used to infer the host color. The results show that stellar templates of 1 and 0.625~Gyr can match the sample color at $z<1.44$ and $z>1.44$, respectively (see Figure 5 in D20). These best-fit models are used to estimate the stellar masses of the host galaxies. \mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citet{Vestergaard2006}, in a consistent manner to that adopted for HSC sample. \red{The mass ranges for the HST sample are log(\smass) $\in$ [9.5, 11.0] $M_{\odot}$, and log(\mbh) $\in$  [7.5, 9.0] $M_{\odot}$)}.
 We refer the reader to D20 for a more detailed description of the analysis.

@@

\begin{deluxetable*}{lccccc}
\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
}
\startdata
box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
\cline{1-6}
{\bf mass resolution} \\
 dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
 baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
\cline{1-6}
{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ \red{radiative efficiency})} \\
High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
Low acc. mode  & -- & 0.35 $\times$ 0.2 & $\leq0.2 \times$ 0.2 & $\leq0.2 \times$ 0.2 & 1 $\times$ 0.1 \\
Transitions btw. modes & -- & 0.05 & \multicolumn{2}{c}{min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]} & 0.01 \\
\cline{1-6}
AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
\enddata
\tablecomments{In the penultimate row, $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$. $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$. \todo{Aklant: The $\leq$ sign in the low accretion feedback mode of TNG is also not clear. Is it a fixed value or a distribution?} \todo{Aklant: Referee asks us whether the same radiative efficiency is used to compute AGN luminosity in all the simulations. But we already show these values in Table 1, which are different, don't we?}
}
\end{deluxetable*}

@@

\red{Note that each simulation adopt either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF. To make a self-consistent comparison, we ensure that the adopted IMF for the simulation and the observation are the consistent and to be the same. For numerical simulation, the mass is the base materials which are IMF independent. Actually, this assumption is still needed so that one can convert the observed luminosity to stellar mass to perform the comparison.}

\subsection{{\tt MassiveBlackII} (MBII)}\label{subsec:MBII}
MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $(142.7~\mathrm{cMpc})^3$
and $2\times1792^3$ particles. \todo{Aklant: answer what is the factor 2 here. A twin box with 1793$^3$ each?} The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}. For dark matter and gas, the mass resolutions are $1.57\times 10^7~M_{\odot}$ and $3.14\times 10^6~M_{\odot}$, respectively. The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process~\citep{2005Natur.433..604D}. Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}. Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.

@@

As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.
We adopt this definition of stellar masses for all \red{larger-scale cosmological} simulations described in the following sections, \red{except for Horizon-AGN which use total mass (see Section~\ref{subsec:Horizon}) for details.}  Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure. Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within the Petrosian radii in observational studies~\citep{Schaye2015}. For further details of MBII simulation, we refer the reader to~\citet{Khandai2015}.

@@

The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at irregular intervals between which the BH mass grows by a fixed fraction. \todo{Aklant: Referee asks are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs? does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN. As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy \red{stellar mass}. %, assuming a \cite{2003PASP..115..763C} IMF.

\subsection{IllustrisTNG}
{\it The Next Generation Illustris Simulations} \red{(IllustrisTNG, hereafter, TNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018}} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes. It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations. \red{Note that TNG simulations employ a modified version of the Bondi formalism, with $c_s$ explicitly including a B term for these magneto-hydro simulations.}

@@

The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$. %A Salpeter IMF is assumed. 
\red{Stellar feedback} is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.

@@

We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.  Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbours. Only galaxies with more than 50 particles are considered. \red{Identified with this approach, for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture. The Horizon-AGN's stellar mass by this definition is commonly used, whose stellar mass function is known} in \citet{2017MNRAS.467.4739K} to be in good agreement with observations.
%\todo{Mention that the \smass.}

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.4\textwidth]{HSC_selection_MBII.png}}
{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.4\textwidth]{HST_selection_MBII.png}}
\end{tabular}
\caption{\label{fig:selection}Demonstration of AGN selection using MBII. {\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) \red{for sample at redshift $z=0.6$}. A matched HSC sample is shown by the orange data points. The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space. \red{Note that this is the first  step of the sample selection. We future use AGN magnitude cut to assure that the simulation sample present similar $L_{\rm bol}$ distribution (e.g., see Figure~\ref{fig:offsets_nochange}-left) and \mbh\ distribution with the observation. We then use the same \smass\ cut to collect the final sample.}
{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
% For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines. % \todo{No mention of the redshift in Fig.2}
}
\end{figure*}

@@

For dark matter halos that merge with a larger halo, the impact of dynamical friction is assessed to define whether the halo will survive as a satellite or sink to the center of the dominant galaxy which increases its mass. The binary interactions (fly-bys and mergers), among satellite sub-halos, are  also described by the model. In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}. The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; \todo{Nicola: the link between BH feeding and star formation channels in this sentence is not clear.} (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion). The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase. %A Salpeter IMF is adopted in the SAM simulation. 
\red{A $\Lambda$CDM power} spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter 
$\Omega_b=0.04$, a dark energy density parameter $\Omega_\Lambda=0.7$, and a Hubble constant $h$=0.7 is adopted.
